%!TeX program = pdflatex
% Drew Van Kuiken's Curriculum Vitae
% Email: drew.van.kuiken@unc.edu
% Web: https://drewvankuiken.github.io/

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage{xcolor}
\usepackage{sectsty}

% what is your name?
\newcommand{\myname}{Drew Van Kuiken}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
	left=1.0in,
	top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

\definecolor{CarolinaBlue}{RGB}{75, 156, 211} % define Carolina Blue
\sectionfont{\color{CarolinaBlue}\fontsize{12}{15}\selectfont}
%\sectionfont{}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
			\setlength{\parskip}{0em}
			\setlength{\itemsep}{\listitemspace}
			\setlength{\parsep}{\listitemspace}}}
	{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
	labelindent=0em,
	topsep=0em,
	partopsep=0em,
	itemsep=\listitemspace,
	parsep=\listitemspace,
	font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
	colorlinks  = true,
	urlcolor    = black,
	citecolor   = black,
	linkcolor   = black,
	pdfauthor   = {\myname},
	pdfkeywords = {innovation, economics of innovation, industrial organization, IO},
	pdftitle    = {\myname: Curriculum Vitae},
	pdfsubject  = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\begin{document}
	\raggedright{}
	
	% display your name as the document title
	\namefont{\myname}
	
	% affiliation and contact info blocks
	\vspace{1em}
	\begin{minipage}[t]{0.700\textwidth}
		% current primary affiliation, left-aligned
		Department of Economics \\
		University of North Carolina - Chapel Hill
	\end{minipage}
	\begin{minipage}[t]{0.295\textwidth}
		% contact info details, right-aligned
		\flushright{}
		\href{mailto:drew.van.kuiken@unc.edu}{drew.van.kuiken@unc.edu} \\
		+1 973 525 7242 \\
		\href{https://drewvankuiken.github.io}{drewvankuiken.github.io}
	\end{minipage}
	
	
	\section*{Education}
	
	\begin{tablist}
		
		\item[Ph.D.] \tab{}Economics \\
		University of North Carolina - Chapel Hill, 2026 (expected) \\
		Field: Industrial Organization, Advisor: Jon Williams
		\item[B.A.]  \tab{}Economics, Government \\
		Bowdoin College, 2017
		
	\end{tablist}
		
	\section*{Research Interests}
	
	\begin{itemize}
		
		\item Industrial Organization, Environmental Economics, Economics of Innovation 
		
	\end{itemize}

    \section*{Research}

    \begin{itemize}
        \item ``Should I Stay or Should I Go? An Empirical Analysis of Consumer Behavior Using Airline Web-Traffic Data'' with Alex Marsh, Garrett Scott, and Jon Williams. \textit{Conditionally accepted} at \textit{Economics of Transportation}
        \begin{quote}
			\textbf{Abstract}: We analyze consumer search and purchase behavior in response to airline revenue-management practices using data from a major carrier's website and Google Flights. We first describe patterns in search timing, purchase decisions, and paid fares. Then we estimate a multinomial logistic regression to identify factors driving search timing, finding that single adults with loyalty status, especially booking one-way nonstop itineraries, tend to search closer to departure. Next, we use a binary logistic model of conversions of searches to sales, showing that competitors' prices and changing customer composition explain rising conversion probabilities as departure nears. Finally, using a fixed-effects regression, we reveal how search and booking patterns affect prices paid. Late-arriving travelers, particularly single adults with loyalty status, pay substantially more, consistent with the airline's pricing strategies that segment more inelastic customers. Overall, our findings underscore how revenue-management, competitor fares, and consumer characteristics jointly shape online search and purchase behavior.
		\end{quote}
        \item ``Product Quality and Consolidation'' with Nate Miller, Nick Rupp, and Jon Williams
    \end{itemize}

	\section*{Teaching Experience}
	
	\begin{tablist}
        \item[Professor] \tab{}ECON 370: Economic Applications of Data Science. Fall 2024.
		\item[TA] \tab{}ECON 410: Intermediate Microeconomics. Fall 2023.
	\end{tablist}

    \section*{Conferences}
	
	\begin{itemize}
        \item Southern Economic Association (2023, 2024)
	\end{itemize}
	

	\section*{Awards}
	
	\begin{tablist}
        \item[2025] \tab{}Center for Regulatory and Industry Studies, Summer Fellowship
		\item[2024] \tab{}Center for Regulatory and Industry Studies, Summer Fellowship
		\item[2023] \tab{}Robert E. Gallman Graduate Student Scholarship, UNC Department of Economics
		\item[2021--26] \tab{}UNC Graduate Economics Fellowship
	\end{tablist}
	
	
	\section*{Technical Skills}
	
	Matlab, Python, R, Stata
	
	\section*{Service}
	
	UNC Economics Graduate Student Association Co-President (2023-2024)
	
	%\pagenumbering{gobble}	
	
\end{document}
